Extending Morphological Chains with Supervised Learning and Cross-Language Features

### 2015-12-10 paper/paper.tex
stuff

\begin{table*}
    \begin{center}
        \begin{tabular}{ | l | l | l | l | l |}
            \hline
            Language & Method & Precision & Recall & F1 \\ \hline
                     & \citeauthor{Narasimhan15} & 0.807 & 0.722 & 0.762 \\ 
                     & Unsupervised (Baseline) & 0.664  & 0.649 & 0.656 \\ 
            English & Semi-supervised ($\lambda=15$) & 0.892 & 0.762 & 0.822 \\ 
                    & Two language unsupervised & 0.432 & 0.652 & 0.520 \\ 
                    & Two language semi-supervised & 0.449 & 0.759 & 0.564 \\ \hline
                    & \citeauthor{Narasimhan15} & 0.743 & 0.520 & 0.612 \\ 
                    & Unsupervised (Baseline) & 0.675 & 0.371 & 0.479 \\ 
            Turkish & Semi-supervised ($\lambda=50$) & 0.763 & 0.642 & 0.697 \\ 
        \end{tabular}
        \caption{Accuracies of Various Models. For our model, we used the top 48000 English words in the wordlist,
        and the MorphoChallenge 2010 Train/Development sets for training and testing, respectively.}
    \end{center}
\end{table*}

@@

\section{Results}
We found that utilizing information from the gold segmentations, we were able to substantially increase our
performance, from an accuracy of 65.5\% to 81.7\% with English, and from 47.9\% to 70.3\% with Turkish.
This is a substantial but expected increase; observing the unsupervised model reveals that it performs
many single-letter

>>>>

\begin{table*}
    \begin{center}
        \begin{tabular}{ | l | l | l | l | l |}
            \hline
            Language & Method & Precision & Recall & F1 \\ \hline
                     & \citeauthor{Narasimhan15} & 0.807 & 0.722 & 0.762 \\ 
                     & Unsupervised (Baseline) & 0.664  & 0.649 & 0.656 \\ 
            English & Semi-supervised ($\lambda=15$) & 0.892 & 0.762 & 0.822 \\ 
                    & Two language unsupervised & 0.432 & 0.652 & 0.520 \\ 
                    & Two language semi-supervised & 0.449 & 0.759 & 0.564 \\ \hline
                    & \citeauthor{Narasimhan15} & 0.743 & 0.520 & 0.612 \\ 
            Turkish & Unsupervised (Baseline) & 0.675 & 0.371 & 0.479 \\ 
                    & Semi-supervised ($\lambda=50$) & 0.763 & 0.642 & 0.697 \\ \hline
        \end{tabular}
        \caption{Accuracies of Various Models. For our model, we used the top 48000 English words in the wordlist,
        and the MorphoChallenge 2010 Train/Development sets for training and testing, respectively.}
    \end{center}
\end{table*}

@@

\section{Results}
We found that utilizing information from the gold segmentations, we were able to substantially increase our
performance, from an accuracy of 65.5\% to 81.7\% with English, and from 47.9\% to 69.7\% with Turkish.
This is a substantial but expected increase; observing the unsupervised model reveals that it performs
many segmentations with nonexistent affixes, which are rectified by providing input about known affixes.
